Supplemental Material: Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling.

### 2020-01-27 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Fixed missing reference
New figures and small edits

\title{Supporting Information: Capturing Subdiffusive Solute Dynamics and 
Predicting Selectivity in Nanoscale Pores with Time Series Modeling.}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  %MRS8: See discussion in main text on ``the AD model''
  %MRS8: fig:msddm_fpt_fits is commented out?  Or xr not working should this be main text?
  %BJC8: yeah because 
  In Figure~\ref{fig:ad_fpt_fits} 
  %and~\ref{fig:msddm_fpt_fits},  % BJC8: didn't do solute flux with MSDDM so why mention
  we demonstrate
  the high quality of our analytical fits of Equation~\ref{eqn:passage_times} to 
  the distribution of solute first passage times derived from both the AD
  and MSDDM models. 
  %The histograms in Figure~\ref{fig:msddm_fpt_fits} are 
  %relatively noisy because we only generated 1000 realizations of the MSDDM 
  %versus 10000 of the AD model. 
  In Figure~\ref{fig:flux_curve_sensitivity}, we
  %justify our use of fewer MSDDM realizations by using subsets of the 10000 AD 
%  model realizations to 
  show that one only needs as few as 100 independent trajectory
  realizations at each pore length in order to reliably fit Equation~\ref{eqn:passage_times}
  to the passage time distributions.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_URE.pdf}
  \caption{urea}\label{fig:Nsensitivity_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_ACH.pdf}
  \caption{acetic acid}\label{fig:Nsensitivity_ACH}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_GCL.pdf}
  \caption{ethylene glycol}\label{fig:Nsensitivity_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_MET.pdf}
  \caption{mehtanol}\label{fig:Nsensitivity_MET}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
  the flux values decreases as we add more independent trajectories.
  }\label{fig:flux_curve_sensitivity}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_URE.pdf}
  \caption{urea}\label{fig:Asensitivity_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_ACH.pdf}
  \caption{acetic acid}\label{fig:Asensitivity_ACH}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_GCL.pdf}
  \caption{ethylene glycol}\label{fig:Asensitivity_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_MET.pdf}
  \caption{mehtanol}\label{fig:Asensitivity_MET}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
  the flux values decreases as we add more independent trajectories.
  }\label{fig:A_sensitivity}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_URE.pdf}
  \caption{urea}\label{fig:betasensitivity_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_ACH.pdf}
  \caption{acetic acid}\label{fig:betasensitivity_ACH}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_GCL.pdf}
  \caption{ethylene glycol}\label{fig:betasensitivity_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_MET.pdf}
  \caption{mehtanol}\label{fig:betasensitivity_MET}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
  the flux values decreases as we add more independent trajectories.
  }\label{fig:beta_sensitivity}
  \end{figure}

>>>>

\title{Supplemental Material: Capturing Subdiffusive Solute Dynamics and 
Predicting Selectivity in Nanoscale Pores with Time Series Modeling.}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  %MRS8: See discussion in main text on ``the AD model''
  %MRS8: fig:msddm_fpt_fits is commented out?  Or xr not working should this be main text?
  %BJC8: yeah because 
  In Figure~\ref{fig:ad_fpt_fits} 
  %and~\ref{fig:msddm_fpt_fits},  % BJC8: didn't do solute flux with MSDDM so why mention
  we demonstrate
  the high quality of our analytical fits of Equation~\ref{eqn:passage_times} to 
  the distribution of solute first passage times derived from both the AD
  and MSDDM models. 
  %The histograms in Figure~\ref{fig:msddm_fpt_fits} are 
  %relatively noisy because we only generated 1000 realizations of the MSDDM 
  %versus 10000 of the AD model. 
  In Figures~\ref{fig:flux_curve_sensitivity}--~\ref{fig:beta_sensitivity}, we
  %justify our use of fewer MSDDM realizations by using subsets of the 10000 AD 
%  model realizations to 
  show that one can reliably fit Equation~\ref{eqn:passage_times}
  to the passage time distributions with as few as 100 independent trajectory
  realizations at each pore length. For higher precision, we recommend using at least
  1000 trajectories.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_URE.pdf}
  \caption{urea}\label{fig:Nsensitivity_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_ACH.pdf}
  \caption{acetic acid}\label{fig:Nsensitivity_ACH}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_GCL.pdf}
  \caption{ethylene glycol}\label{fig:Nsensitivity_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_MET.pdf}
  \caption{methanol}\label{fig:Nsensitivity_MET}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
  the flux values decreases as we add more independent trajectories.
  }\label{fig:flux_curve_sensitivity}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_URE.pdf}
  \caption{urea}\label{fig:Asensitivity_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_ACH.pdf}
  \caption{acetic acid}\label{fig:Asensitivity_ACH}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_GCL.pdf}
  \caption{ethylene glycol}\label{fig:Asensitivity_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_MET.pdf}
  \caption{methanol}\label{fig:Asensitivity_MET}
  \end{subfigure}
  \caption{The flux scaling parameter ($A$) can be reliably estimated using
  as few as 100 independent realizations of the sFBMcut AD model. To estimate
  $A$, we fit Equation~\ref{M-eqn:flux_decay} of the main text to a series of
  flux measurements made with 10, 15, 20, 25, 30, 35, 40, 45 and 50 nm pores (see
  Figure~\ref{M-fig:flux_curves_ad} of the main text).
  }\label{fig:A_sensitivity}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_URE.pdf}
  \caption{urea}\label{fig:betasensitivity_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_ACH.pdf}
  \caption{acetic acid}\label{fig:betasensitivity_ACH}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_GCL.pdf}
  \caption{ethylene glycol}\label{fig:betasensitivity_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_MET.pdf}
  \caption{methanol}\label{fig:betasensitivity_MET}
  \end{subfigure}
  \caption{Similar to $A$, the parameter which describes the scaling of solute
  flux with pore length, $\beta$, can be reliably estimated using as few as 100
  independent realizations of the sFBMcut AD model. We estimated $\beta$ and
  $A$ simultaneously as described in Figure~\ref{fig:A_sensitivity}.
  }\label{fig:beta_sensitivity}
  \end{figure}
